Detecting Hate Speech with GPT-3

### 2022-02-28 outputs/documents/paper.Rmd
Final proof reading edits

```{r profanity}
# Table of profane words/substrings and misspellings introduced
profanity <- tibble(string = c("nigg", "fuck", "whore", "kill", "rape", "die", "bitch"),
                    edit = c("n1gg, nig, n*gg, n-gg",
                             "fck, phuck, f*ck, f-ck",
                             "wh0re, whor3, wh0r3, wh*re, wh-re",
                             "k1ll, kil, k-ll, k*ll",
                             "r@pe, rap3, r@p3, rap, r*pe, r-pe",
                             "d1e, di3, d13, dye, d*e, d-e",
                             "b1tch, bich, bithc, bicht, b*tch, b-tch"))
profanity %>%
  knitr::kable(caption="Profane strings used to identify comments to test impacts of misspelling and censorship on hate speech classificiation",
               booktabs = TRUE,
               col.names = c("Original", "Edits"))
```

>>>>

```{r profanity}
# Table of profane words/substrings and misspellings introduced
profanity <- tibble(string = c("nigg", "fuck", "whore", "kill", "rape", "die", "bitch"),
                    edit = c("n1gg, nig, n*gg, n-gg",
                             "fck, phuck, f*ck, f-ck",
                             "wh0re, whor3, wh0r3, wh*re, wh-re",
                             "k1ll, kil, k-ll, k*ll",
                             "r@pe, rap3, r@p3, rap, r*pe, r-pe",
                             "d1e, di3, d13, dye, d*e, d-e",
                             "b1tch, bich, bithc, bicht, b*tch, b-tch"))
profanity %>%
  knitr::kable(caption="Strings used to extract comments with profanity and edits introduced to test impacts of misspelling and censorship on hate speech classificiation",
               booktabs = TRUE,
               col.names = c("Original", "Edits"))
```
